The Dynamics of Anthropomorphic Effects in Human-Robot Interaction

### 2014-03-26 paper.tex
diverse understandings of anthropomorphism

Literature on anthropomorphism (the social phenomenon) in robotics as well as on
anthropomorphic design of robots is quite diverse. There exist different understandings of what anthropomorphism is, and consequently, one strives hard to
extract a coherent conclusion.

One reason for why anthropomorphism is defined in different ways might be that it
is a concept that is studied in very different domains that might each
integrate diverse or even contradictory understandings, or simply refer to
different things.
However, one conflict is that, despite the fact that there is no commonly accepted
definition, and also the terminology is not clear, the terms
\textit{anthropomorphism}, \textit{anthropomorphic} or \textit{human-like} are
often used as if their meanings were clear and agreed upon
\cite{persson_anthropomorphism_2000}. Duffy \cite{duffy_anthropomorphism_2002}
argues that these terms might even be misused (in accordance with
\cite{epley_when_2008}). For instance, some researchers refer to \textit{"the
robot's level of anthropomorphism"} \cite{bartneck_is_2007}, whereas others
argue that the system or artifact itself does not "contain anthropomorphism"
\textit{per se} but only gives rise to the process of anthropomorphizing in a
given user and situation. Consequently, Persson \textit{et al.} conclude that
anthropomorphism emerges in the \textit{interaction} between the technology and
the user \cite{persson_anthropomorphism_2000}. We will come back to this view later, in the summary of this section (Subsection \ref{sec:multi-factors}).

Paradoxically, human's tendency to anthropomorphize non-human agents (such as
robots) is commonly observed but at the same time it is rather poorly understood
\cite{epley_seeing_2007}. There might be several reasons. First, probably
because the phenomenon itself has been found to be very complex though sometimes
subtle and as such hard to study. Second, the rather poor (or controversial)
understanding, might also be due to the limited reliability of some findings (or
interpretations) from experiments investigating anthropomorphism. Most of the
experiments that investigate anthropomorphism in robotics are conducted in
controlled lab-settings during short-term human-robot interactions. This
experimental setting can be critical when studying a social phenomenon like
anthropomorphism and possibly lead to over-interpretations. Some studies (e.g.
exploring characteristics of the "uncanny valley") also seem to contrast two or
more different anthropomorphic or mechanical systems that might not be
appropriate for comparison given the complex context. Others might also use
empirical methods inappropriate for the given research question which leads to
inaccurate results. \hl{say more}

@@

@@

Not only \cite{epley_when_2008} and \cite{duffy_anthropomorphism_2002} but also others have noticed that anthropomorphism is a very complex phenomenon -- itself and in how it can be understood. This holds implications for the study of anthropomorphism (to what we will come back later in this article \hl{(REF to studying / measuring anthropomorphism)}.
A common formal ground is missing so far; however, it is important to be clear about what exactly we mean when using the term anthropomorphism.

@@

In sum, this branch of research suggests that anthropomorphism implies that
people thoughtfully develop a mental model of agents in their environment and
that they make inferences about these agents based on what is familiar to them
-- themselves, humans and human behavior. This understanding builds on a
person's ability to attribute mental states to oneself and others, which is
called \textit{Theory of Mind}~\citep{premack1978does}. A theory of mind for
other agents enables us to attribute intentionality to those agents
\citep{leslie_pretense_1987,admoni_multi-category_2012}. The link between this
tendency to thoughtfully anthropomorphize and the engagement in the attribution
of mental states to other humans were recently demonstrated at the brain
level~\citep{cullen2013individual}.

@@

\subsection{Measuring anthropomorphism}
\label{measuring}

>>>>

Literature on anthropomorphism is quite diverse. There exist different understandings of what 
anthropomorphism is. 
One reason for this might be that anthropomorphism
is a concept that is studied in very different domains that might each
integrate diverse or even contradictory understandings, or simply refer to
different things.
However, the conflict is that, despite the fact that there is no commonly accepted
definition, the terms
\textit{anthropomorphism}, \textit{anthropomorphic} or \textit{human-like} are
often used as if their meanings were clear and agreed upon
\citep{persson_anthropomorphism_2000}. Duffy \cite{duffy_anthropomorphism_2002} and \cite{epley_when_2008}
argue that these terms might even be misused. For instance, some researchers refer to \textit{"the
robot's level of anthropomorphism"} \cite{bartneck_is_2007}, whereas others
disagree to such a statement because they argue that the system or artifact itself does not \textit{"contain anthropomorphism" per se} but only gives rise to the process of anthropomorphizing in a
given user and situation. Consequently, \cite{persson_anthropomorphism_2000} conclude that
anthropomorphism emerges in the \textit{interaction} between the technology and
the user, and has to be understood as such. 
We will come back to this view later, in the summary of this section (Subsection \ref{sec:multi-factors}).

Paradoxically, while human's tendency to anthropomorphize is commonly observed it is 
at the same time still rather poorly understood
\cite{epley_seeing_2007}. The phenomenon itself has been found to be very complex though sometimes
subtle and as such hard to study.
Also, the methods and measurements applied to study anthropomorphism appear insufficient, when applying a holistic understanding of anthropomorphism emerging from an interaction between a human user and a robot, for instance. Our point here is that to study a phenomenon as complex as anthropomorphism, we believe that one needs to take into account many factors (see Section \ref{sec:multi-factors}), besides looking at the human-like design of the artifact.
However, most of the
experiments that investigate anthropomorphism in robotics are conducted in
controlled lab-settings during short-term human-robot interactions. This
experimental setting can be critical for studying
anthropomorphism and findings might possibly lead to interpretations that would not be generalizable to natural settings or real interaction scenarios.\footnote{For instance, some studies are about showing pictures of different robots to human subjects and then asking them how "human-like" they would rate these robots. What points of reference do the participants have in this setting? What can you really tell from a picture? I found that some normal people totally misinterpret the size / height of a robot, when it is not indicated. Also, when showing only pictures, movements, behaviors, materials, and so forth are totally disregarded. However, these aspects are also crucial to assess how "human-like" a robot appears. Last but not least, it has been found that "human-likeness" is a quite diverse and abstract term that includes many things. Instead of asking such a big question, \cite{kahn_jr._robotic_2006} suggest to ask for more concrete constructs that are typical or unique of the concept of "human-likeness", such as being hungry or feeling guilty. For instance, \cite{ruijten_introducing_2014} propose a 25 concrete questions to measure anthropomorphism along a scale that accounts for lower and higher levels of it. \hl{(let's move this to the measurement section at the end.)}}
Some studies (e.g.
exploring characteristics of the "uncanny valley") also seem to contrast two or
more different anthropomorphic or mechanical systems that might not be
appropriate for comparison given the complex context. Others might also use
empirical methods inappropriate for the given research question which leads to
inaccurate results. \hl{say more}

@@

Not only \cite{epley_when_2008} and \cite{duffy_anthropomorphism_2002} but also others have noticed that anthropomorphism is a very complex phenomenon -- itself and in how it can be understood. This raises question how to study and operationalize anthropomorphism in an appropriate way (see Section \ref{sec:measuring}}.
A common formal ground is missing so far; however, it is important to be clear about what exactly we mean when using the term anthropomorphism.

@@

@@

In sum, this branch of research suggests that anthropomorphism implies that people thoughtfully develop a mental model of agents in their environment and that they make inferences about these agents based on what is familiar to them -- themselves, humans and human behavior. This understanding builds on a person's ability to attribute mental states to oneself and others, which is called \textit{Theory of Mind}~\citep{Premack1978}. A theory of mind for other agents enables us to attribute intentionality to those agents \citep{leslie_pretense_1987,admoni_multi-category_2012}. The link between this tendency to thoughtfully anthropomorphize and the engagement in the attribution of mental states to other humans were recently demonstrated at the brain level~\citep{cullen2013individual}.

@@

\subsection{Measuring anthropomorphism}
\label{sec:measuring}
